Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-08 article/article.Rmd
Commit 2024-06-08 07:13

On multiple sites, cloud enhancements (CE) have been reported to be able to briefly
exceed the value of the solar constant, resulting of clearness indices above unit. A
summary of extreme enchantment cases (ECE) has been compiled by @Martins2022. There
are also; some practical implications of the cloud enchantments.  The intensity and
duration of enhancements can effect the efficiency and stability of photovoltaic
power production [@Lappalainen2020; @Jaervelae2020]; while ECEs have the potential to
compromise the integrity of photovoltaic plants infrastructure [@DoNascimento2019].
It has also been demonstrated that these events can interfere in the comparison of
ground-based and satellite observations [@Damiani2018].  Global warming has likely
affected cloud coverage in the last few decades. @Liu2023 reported increases in cloud
cover over the tropical and subtropical oceans and decreases over most continents,
while @Dong2022 reported decreases over North America and Europe. To our knowledge,
there is no evidence on whether this trend has affected also the number and strength
of CE events.

>>>>

On multiple sites, cloud enhancements (CE) have been reported to be able to briefly
exceed the value of the solar constant, resulting of clearness indices above unit. A
summary of extreme enchantment cases (ECE) has been compiled by @Martins2022. There
are also; some practical implications of the cloud enchantments.  The intensity and
duration of enhancements can effect the efficiency and stability of photovoltaic
power production [@Lappalainen2020; @Jaervelae2020]; while ECEs have the potential to
compromise the integrity of photovoltaic plants infrastructure [@DoNascimento2019].
It has also been demonstrated that these events can interfere in the comparison of
ground-based and satellite observations [@Damiani2018].  Global warming has likely
affected cloud coverage in the last few decades. @Liu2023 reported increases in cloud
cover over the tropical and subtropical oceans and decreases over most continents,
while @Dong2023 reported decreases over North America and Europe. To our knowledge,
there is no evidence on whether this trend has affected also the number and strength
of CE events.
